### 2014-03-01 paper/real.tex
minor

Although other sandboxing mechanisms can be used in place of Dune, we
believe Dune's hardware protection mechanism allow us to provide a 
concrete implementation that is simpler to reason about.
%
To this end, the combined language of Section~\ref{sec:retrofict}
corresponds to C with the additional IFC syscalls.
%
Creating a new task with the |fork| syscall ensures that no memory is
shared, by defining |kappa(tS) = tS0|, where |tS0| is the set of pages
we copy to bootstrap the lightweight process.
%
Similarly, sending a message with |send| results in a copying the
pages to our (trusted) runtime, and, then the (untrusted) receiver.
%
Of course, a more efficient message-passing approach, such as that of
Singularity~\tocite{}, which simply passes a pointer to data the
receiver at the cost of revoking the sender's access to the pages is
also possible.

>>>>

Although other sandboxing mechanisms can be used in place of Dune, we
believe Dune's hardware protection mechanism allow us to provide a 
concrete implementation that is simpler to reason about.
%
The ability to provide a new syscall interface allows us to precisely
define the combined language of Section~\ref{sec:retrofit} as C with
(only) IFC syscalls.
%
Page tables limits what memory a task can access; hence, we can ensure
that new task created with the |fork| syscall will not have any shared
memory, i.e., we effectively define |kappa(tS) = tS0|, where |tS0| is
the set of pages necessary in bootstrap a lightweight process.
%
Similarly, control over page tables and protection bits allows us to
define a |send| syscall that copies pages to our
(trusted) runtime queue; and, correspondingly, a |recv| that copies
the pages from the runtime queue to the (untrusted) receiver.
%
Since C is not memory safe, conditions on these syscalls are
meaningless.
%
Of course, a more efficient message-passing approach, such as that of
Singularity~\tocite{}, which simply passes a pointer to data the
receiver at the cost of revoking the sender's access to the pages is
also possible.
%
However, since we do not consider the isomorphism condition for this,
we do not discuss it further.
